The \dealii Library, Version 9.4

### 2022-06-24 9.4/paper.tex
fix typo
improve readability of tables

  \begin{tabular}{|c|c|c|c|}
  \hline
Version       & MPI routine used            & 1 file, striping 16 & 16 files, no striping \\
\hline
\dealii{} 9.3 & \texttt{MPI\_File\_write\_ordered()} & 3 GB/s              & 15 GB/s              \\
\dealii{} 9.4 & \texttt{MPI\_File\_write\_at\_all()} & 17 GB/s             & 21 GB/s
\\
\hline
\end{tabular}

>>>>

  \begin{tabular}{llcc}
    \toprule
    Version       & MPI routine used                     & 1 file, striping 16 & 16 files, no striping \\[0.3em]
    \dealii{} 9.3 & \texttt{MPI\_File\_write\_ordered()} & 3 GB/s              & 15 GB/s               \\
    \dealii{} 9.4 & \texttt{MPI\_File\_write\_at\_all()} & 17 GB/s             & 21 GB/s               \\
    \bottomrule
\end{tabular}
